Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
Corrected again

\begin{table*}[t]
	\caption{
		\label{tab:1}
		Comparison between G(PO)MDP and SVRPG on different tasks. Average return over the whole learning process is reported, together with normalized standard deviation and 90\% confidence intervals.}
	\centering
	\begin{tabular}{@{}lccccccc@{}} 
		\toprule
		\phantom{abc} & \multicolumn{3}{c}{G(PO)MDP} & \phantom{abc} & \multicolumn{3}{c}{SVRPG} \\
		\cmidrule{2-4} \cmidrule{6-8}
		\phantom{abc} & Avg Return & Norm. Std & C.I. & \phantom{abc}
		& Avg Return & Norm. Std & C.I.
		\\\cmidrule{2-8}
		Cart-pole & 618.49 & 21.09 & [579.82, 657.16] & \phantom{abc} 
		& \textbf{736.31} & 16.51 & [706.04, 766.57] \\ 
		\phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} \\
		Swimmer & 39.86 & 3.84 & [31.18, \:\:\: 48.53] & \phantom{abc} & 49.60 & 3.27 & [43.60, \:\:\: 55.60]\\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
	\caption{
		\label{tab:1}
		Comparison between G(PO)MDP and SVRPG on different tasks. Average return over the whole learning process is reported, together with normalized standard deviation and 90\% confidence intervals.}
	\centering
	\begin{tabular}{@{}lccccccc@{}} 
		\toprule
		\phantom{abc} & \multicolumn{3}{c}{G(PO)MDP} & \phantom{abc} & \multicolumn{3}{c}{SVRPG} \\
		\cmidrule{2-4} \cmidrule{6-8}
		\phantom{abc} & Avg Return & Norm. Std & C.I. & \phantom{abc}
		& Avg Return & Norm. Std & C.I.
		\\\cmidrule{2-8}
		Cart-pole & 618.49 & 21.09 & [579.82, 657.16] & \phantom{abc} 
		& \textbf{736.31} & 16.51 & [706.04, 766.57] \\ 
		\phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} & \phantom{abc} \\
		Swimmer & 39.86 & 3.84 & [32.82, \:\:\: 46.89] & \phantom{abc} & 49.60 & 3.27 & [43.60, \:\:\: 55.60]\\
		\bottomrule
	\end{tabular}
\end{table*}
